\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
show microsecond correctly

\subsection{Experiment Result Analysis}
Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 \textmu s in idle situation, 18 \textmu s in stressed situation. And in the worse case, the latency is below 50 \textmu s. Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 \textmu s and can't guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 us in stressed condition).  As for mainline Linux, the max latency easily exceeds 1 ms. When comparing the performance of Xenomai-3 to Xenomai-2, we can see that the stats in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.

>>>>

\subsection{Experiment Result Analysis}
Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 \textmu s in idle condition, 18 \textmu s in stressed condition. And in the worse case, the latency is below 50 \textmu s. Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 \textmu s, which means it can not guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 \textmu s in stressed condition).  As for mainline Linux, the max latency easily exceeds 1 ms. When comparing the performance of Xenomai 3 to Xenomai 2, we can see that the statistics in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.
